Characterizing dynamical transitions by statistical complexity measures based on ordinal pattern transition networks

### 2021-01-26 manuscript_Huang.tex
revision almost done.

{\color{red} @ Reik: I'm not sure whether to include the following discussion in the main text as suggested by the referee. The discriminatory power of different SCMs have been further compared in Fig. \ref{fig:CHlogCmax}, which characterize the distances to the maximal complexity $\mathcal{C}_{max}$. In particular, for a given $\mathcal{H}$ we compute a normalized complexity $\mathcal{C}^{N} = (\mathcal{C} - \mathcal{C}_{min}) / (\mathcal{C}_{max} - \mathcal{C}_{min})$. In turn, $\mathcal{C}^{N}$ is bounded in the interval of $[0, 1]$ and the alignment along $\mathcal{C}_{max}$ is reflected by large values of $\mathcal{C}^{N}$. The results are shown in Fig. \ref{fig:CHlogCmax}. The dots larger than 1 are numerical artefacts Fig. \ref{fig:CHlogCmax}(c) which are due to  improper choice of embeddings when the Logistic map shows high periodic iterations.    
\begin{figure*}
        \centering
        \includegraphics[width=2\columnwidth]{CompEntropyCNormalized_Logistic.pdf}
\caption{(Color online) Three SCMs which are normalized by $\mathcal{C}_{max}$ and $\mathcal{C}_{min}$  at a given $\mathcal{H}$, for the logistic map.  \label{fig:CHlogCmax}}
\end{figure*}
}

@@

{\color{red} For fBM, we can include another figure showing normalized complexity measures by the corresponding $\mathcal{C}_{max}$ and $\mathcal{C}_{min}$ as Fig. \ref{fig:CHlogCmax}. As the embedding dimension $D$ is increased, the dots are more aligned to $\mathcal{C}_{max}$ and extend further to the left half of the complexity--entropy plane. 
\begin{figure*}
        \centering
        \includegraphics[width=2\columnwidth]{CompEntropyCNormalized_fBm.pdf}
\caption{(Color online) Three SCMs which are normalized by $\mathcal{C}_{max}$ and $\mathcal{C}_{min}$  at a given $\mathcal{H}$, for the fractional Brownian motion.  \label{fig:CHlogCmax}}
\end{figure*}
}

>>>>

{\color{red} @ Reik: I'm not sure whether to include the following discussion in the main text as suggested by the referee. The discriminatory power of different SCMs have been further compared in Fig. \ref{fig:CHlogCmax}, which characterize the distances to the maximal complexity $\mathcal{C}_{max}$. In particular, for a given $\mathcal{H}$ we compute a normalized complexity $\mathcal{C}^{N} = (\mathcal{C} - \mathcal{C}_{min}) / (\mathcal{C}_{max} - \mathcal{C}_{min})$. In turn, $\mathcal{C}^{N}$ is bounded in the interval of $[0, 1]$ and the alignment along $\mathcal{C}_{max}$ is reflected by large values of $\mathcal{C}^{N}$. The results are shown in Fig. \ref{fig:CHlogCmax}. The dots larger than 1 are numerical artefacts Fig. \ref{fig:CHlogCmax}(c) which are due to  improper choice of embeddings when the Logistic map shows high periodic iterations.    
\begin{figure*}
        \centering
        \includegraphics[width=2\columnwidth]{CompEntropyCNormalized_Logistic.pdf}
\caption{(Color online) Three SCMs which are normalized by $\mathcal{C}_{max}$ and $\mathcal{C}_{min}$  at a given $\mathcal{H}$, for the logistic map. Embedding dimensions are indicated by legends.  \label{fig:CHlogCmax}}
\end{figure*}
}

@@

{\color{red} For fBM, we show another figure of normalized complexity measures by the corresponding $\mathcal{C}_{max}$ and $\mathcal{C}_{min}$ as Fig. \ref{fig:CHlogCmax}. As the embedding dimension $D$ is increased, the dots are more aligned to $\mathcal{C}_{max}$ and extend further to the left half of the complexity--entropy plane. 
\begin{figure*}
        \centering
        \includegraphics[width=2\columnwidth]{CompEntropyCNormalized_fBm.pdf}
\caption{(Color online) Three SCMs which are normalized by $\mathcal{C}_{max}$ and $\mathcal{C}_{min}$  at a given $\mathcal{H}$, for the fractional Brownian motion.  \label{fig:CHlogCmax}}
\end{figure*}
}
